Who does big team science?

### 2023-09-18 manuscript_scopus.Rmd
fixing author typo

```{r total-authors}
# updated
total_authors <- 510334
avg_authors <- apa_num(49.30516877182394)
sd_authors <- apa_num(212.9786134634032)
min_authors <- 10
med_authors <- 18
max_authors <- 5568
```

>>>>

```{r total-authors}
# updated
total_authors <- 3047067
avg_authors <- apa_num(49.30516877182394)
sd_authors <- apa_num(212.9786134634032)
min_authors <- 10
med_authors <- 18
max_authors <- 5568
```

### 2023-09-18 manuscript_scopus.tex
fixing author typo

The total number of unique authors across all publications was
510334. The mean number of authors per publication was \emph{M} =
49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a
range of 10 to 5568. The median and average
number of authors by subject area are displayed in Figure
\ref{fig:fig-author-year}. In general, the average and median number of
authors increased over time, with the exception of the skew in the
Physical Sciences. Interestingly, the effect in the Physical Sciences
appears to be declining toward the general trends seen in other areas in
the last few decades.

@@

\textbf{Keywords}. Figure \ref{fig:fig-keywords} indicates the most common keywords present for the BTS publications by subject area. The keywords were tokenized into single tokens. Keywords were then lowercased, and all stop words (for example, the, an, of, into, for) were removed. Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.

>>>>

The total number of unique authors across all publications was
3047067. The mean number of authors per publication was \emph{M} =
49.31 (\emph{SD} = 212.98, \emph{Med} = 18) with a
range of 10 to 5568. The median and average
number of authors by subject area are displayed in Figure
\ref{fig:fig-author-year}. In general, the average and median number of
authors increased over time, with the exception of the skew in the
Physical Sciences. Interestingly, the effect in the Physical Sciences
appears to be declining toward the general trends seen in other areas in
the last few decades.

@@

\textbf{Keywords}. Figure \ref{fig:fig-keywords} indicates the most common keywords present for the BTS publications by subject area. The keywords were tokenized into single tokens. Keywords were then lower cased, and all stop words (for example, the, an, of, into, for) were removed. Finally, a frequency count of tokens was tabulated for each subject area, and this count is used to create the final word cloud presented.
